Model to study co-evolution of trade an culture

### 2015-02-23 article.tex
change style to wsc. update bib. still some problems in bib to correct (journal and date missing)

%        File: 20150216ModelDescription.tex
%     Created: lun. févr. 16 11:00  2015 C
% Last Change: lun. févr. 16 11:00  2015 C
%
\documentclass[a4paper]{article}

%%%%lualatex on
%\usepackage{fontspec}

\usepackage{natbib}

\title{Draft Model}
\author{Simon}
\begin{document}
\maketitle

\section{Introduction}
In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire. Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi1957tradeandmarketintheearlyempireseconomiesinhistoryandtheory}). Following \cite{epstein1996growingartificialsocietiessocialsciencefromthebottomup,
lake_trends_2014,
kohler2000dynamicsinhumanandprimatesocietiesagentbasedmodelingofsocialandspatialprocesses,
tesfatsion2003agentbasedcomputationaleconomicsmodelingeconomiesascomplexadaptivesystems} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.

@@

Later it could be used to study other model such as those developed by 
\cite{rubinstein1985equilibriuminamarketwithsequentialbargaining} and to test more general proposal, as those done by \cite{polanyi1957tradeandmarketintheearlyempireseconomiesinhistoryandtheory,
polanyi1977thelivelihoodofman} about the early economical mechanisms.

@@

\bibliographystyle{apalike}
\bibliography{wsc.bib}  
\end{document}

>>>>

\input{wsc15style.tex}     % download from author kit.  Style files for wsc formatting. Don't remove this line - required for generating the final paper!

\documentclass{wscpaperproc}
\usepackage{latexsym}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{mathptmx}

%****************************************************************************
%% AUTHOR: You may want to use some of these packages. (Optional)
%\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amssymb}
%\usepackage{amsbsy}
%\usepackage{amsthm}

\usepackage{xcolor}

\newcommand{\memo}[2]{\textcolor{#1}{#2}}
\newcommand{\added}[2]{\textcolor{#1}{#2}}
%\renewcommand{\memo}[2]{} % uncomment in the final version
%\renewcommand{\added}[2]{#2} % uncomment in the final version
\newcommand{\todo}[1]{\memo{red}{TODO: #1\\}}
\newcommand{\simon}[1]{\memo{green}{Simon: #1\\}}
\newcommand{\jm}[1]{\memo{blue}{JM: #1\\}}
\newcommand{\new}[1]{\added{orange}{#1}}

\begin{document}

\WSCpagesetup{Montanier, Carrignon, and Zerr}

\title{Model to study co-evolution of trade an culture}

\author{Jean-Marc Montanier\\ [12pt]
Barcelona Supercomputing Center\\
Carrer de Jordi Girona, 29, \\
08034 Barcelona, Spain\\
\and
Simon Carrignon\\ [12pt]
Barcelona Supercomputing Center\\
Carrer de Jordi Girona, 29, \\
08034 Barcelona, Spain\\
\and
Fabien Zerr\\ [12pt]
Alsace, Represent
}

\maketitle

\section*{ABSTRACT}
\todo{write an abstract}

In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire. Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire. We think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.

\section{Introduction}
In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire. Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi_trade_1957}). Following \cite{epstein_growing_1996,
lake_trends_2014,
kohler_dynamics_2000,
tesfatsion_agent-based_2003} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.

@@

Later it could be used to study other model such as those developed by 
\cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,
polanyi_livelihood_1977} about the early economical mechanisms.

@@

\bibliographystyle{wsc}
\bibliography{wsc.bib}  
\end{document}
